SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-06-28 scipy-1.0/paper.tex
Second round of revisions for manuscript PR 34 based on reviewer feedback.

\pgfplotsset{compat=newest}

@@

Unit test coverage for most recent code additions / adjustments is quite
respectable, but some of the historical components of the code base
would still benefit from increased test coverage. We are still striving
to increase the number of high-quality SciPy usage tutorials, but our
standard documentation for library features is already in excellent shape.

The low-level Cython code in our library (which interacts with C-level
code and exposes it for Python usage) could use some measure of modernization,
including migration to typed memoryviews to handle NumPy arrays in place
of the older syntax.

Some specific submodules of SciPy would benefit from  attention moving forward.
\texttt{fftpack} has some single-precision floating point errors, a caching bug,
and would benefit from the addition of the Bluestein algorithm. There's also
too much community code duplication with \texttt{numpy.fft}, which
requires clarification of best choices and long-term plans.

@@

For \texttt{scipy.linalg} we need to remove functions that are duplicate with 
\texttt{numpy.linalg}, \texttt{get\_lapack\_funcs} should always use flapack, and
we should continue to wrap more LAPACK functions. Ideally, we'd also
add type-generic wrappers in the Cython BLAS and LAPACK interfaces, and
transform many of the linear algebra routines into gufuncs.

We're planning to remove \texttt{scipy.misc} as a public module, and
rename \texttt{scipy.odr} to \texttt{scipy.regression} or
\texttt{scipy.fitting}, and include \texttt{optimize.curve\_fit}. This 
module will then provide a home for other fitting functionality.
\texttt{scipy.optimize} would benefit from a few more good global optimizers 
as well as large-scale optimizers.

\texttt{scipy.ndimage} should be completely migrated to a data point
model (values on a grid), instead of a pixel model (elements with centers),
both of which have been used in the past, because the former is now
proving more effective in practice. We also need to standardize the
\texttt{scipy.ndimage.morphology} API.

>>>>

\pgfplotsset{compat=newest}
\usepackage{listings}

@@

Unit test coverage for most recent code additions / adjustments is quite
respectable, with overall project test coverage holding steady at
around 76\% for the last six months (Figure~\ref{fig:coverage}),
but some of the historical components of the code base
would still benefit from increased test coverage. We are still striving
to increase the number of high-quality SciPy usage tutorials beyond
our current 15 section offering\cite{SciPy_tutorials}, but our
standard documentation for library features is already in excellent shape.

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{static/coverage-chart}
\caption{\% coverage of the SciPy code base by unit tests over the six
	 months preceding June 28, 2018 as reported by the \texttt{codecov}
	 service. The analysis of lines of source code covered is performed
	 automatically in our continuous integation suite using the
	 \texttt{pytest-cov} and \texttt{gcov} libraries.}
\label{fig:coverage}
\end{figure}

The low-level Cython code in our library (which interacts with C-level
code and exposes it for Python usage) could use some measure of modernization,
including migration to typed memoryviews to handle NumPy arrays instead of
the older syntax:

\begin{lstlisting}[language=Python]
# example of a function that takes a single
# 3 dimesional typed memoryview as an argument
# this allows Cython-level handling of a NumPy
# array object
cpdef int func_new(int[:, :, :] arr):
    pass

# example of the old syntax for handling
# the same scenario
cpdef int func_old(object[int, ndim=3, mode='strided'] arr):
    pass

\end{lstlisting}

\texttt{fftpack} has some single-precision floating point errors, a caching bug,
and would benefit from the addition of the Bluestein algorithm. There's also
too much community code duplication with \texttt{numpy.fft}, which
requires clarification of best choices and long-term plans.

@@

For \texttt{scipy.linalg}, we need to remove functions that are duplicate with 
\texttt{numpy.linalg} unless performance is superior in SciPy,
\texttt{get\_lapack\_funcs} should always use flapack, and
we should continue to wrap more LAPACK functions. Ideally, we'd also
add type-generic wrappers in the Cython BLAS and LAPACK interfaces, and
transform many of the linear algebra routines into gufuncs.

We're planning to remove \texttt{scipy.misc} as a public module, and
rename \texttt{scipy.odr} to \texttt{scipy.regression} or
\texttt{scipy.fitting}, and relocate \texttt{optimize.curve\_fit}. This 
module will then provide a home for other fitting functionality.
\texttt{scipy.optimize} would benefit from a few more good global optimizers 
as well as large-scale optimizers.

\texttt{scipy.ndimage} should be completely migrated to a data point
model (values on a grid), instead of a pixel model (elements with centers),
both of which have been used in the past, because the data point model is now
proving more effective in practice. We also need to standardize the
\texttt{scipy.ndimage.morphology} API.
